Identification and performance of stock-recruitment functions in state

### 2024-02-08 Ecov_study/recruitment_functions/presentation/SRR_presentation.Rmd
cleanup analysis code
fixed obs_error labels (H L reversed in factor statement)

# Sims
## Simulated Data Examples - Ecov and SRR 
```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='40%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'recruit_ecov.pdf') )
```

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='50%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'stock_recruit_no_ecov.pdf') )
```

@@

## Results layout (example)
- Plots show median relative error (filled circle) with 2.5th and 97.5th percentiles
- OM factors as facets (top and right side)
- EM models on the x-axis
- Blue indicates EM=OM (diagonal of first 4 columns w/in facet blocks), incorrect EMs in red

@@

## Projection Summary
- Minimal difference in median bias
- Recruitment is highly uncertain in projections, exacerbated by length of projection
- SSB and Catch also show increased uncertainty in longer projections
- Long projections are expected to be very imprecise, recommend shorter projections
- Tighter quantile range and slightly lower CV for mean SRR

@@

## Recommendations for future research
- Additional fishing histories, including some that include years with F < $F_{MSY}$
- Recruitment random effect trends
- Ecov models with stronger effects, trends, or AR(2) dynamics
- Multivariate ecov processes
- Ecov processes affecting multiple stock parameters, or multiple Ecov processes affecting recruitment (simultaneous or sequential)

@@

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='35%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'abacus_crop.jpg') )
```

>>>>

# Sims
## Simulated Data Examples - Ecov and SRR  recruit_ecov_SRR_noecov

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.width='95%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'recruit_ecov_SRR_noecov.png') )
```

 <!-- ```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='40%', fig.align='center'} -->
 <!-- knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'recruit_ecov.pdf') ) -->
<!-- ``` -->

<!--  ```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='50%', fig.align='center'} -->
<!--  knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'stock_recruit_no_ecov.pdf') ) -->
<!-- ``` -->

@@

## Results layout (example)
- Plots show median relative error (filled circle) with 2.5th and 97.5th percentiles
- OM factors as facets (top and right side)
- EM models on the x-axis
- Blue indicates EM=OM (diagonal of first 4 columns w/in facet blocks)
- Incorrect EMs in red

@@

## Projection Summary
- Minimal difference in median bias (median at most -0.1 for mean SRR)
- Recruitment is highly uncertain in projections, exacerbated by length of projection
- SSB and Catch also show increased uncertainty in longer projections
- Long projections are expected to be very imprecise, recommend shorter projections
- Tighter quantile range and slightly lower CV for mean SRR

@@

## Recommendations for future research
- Additional fishing histories, including some that include years with F < $F_{MSY}$
- Recruitment random effect trends
- Ecov models with stronger effects, trends, or AR(2) dynamics
- Multivariate Ecov processes
- Ecov processes affecting multiple stock parameters, or multiple Ecov processes affecting recruitment (simultaneous or sequential)

@@

```{r, echo=FALSE, message=FALSE, warnings=FALSE, out.height='50%', fig.align='center'}
 knitr::include_graphics(file.path(here::here(), 'Ecov_study','recruitment_functions', 'presentation', 'abacus_crop.jpg') )
```
